---
title: "roultier"
author: "Ben Gonzalez"
date: "11/21/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Put the title of your vignette here}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  lines <- options$output.lines
  if (is.null(lines)) {
    return(hook_output(x, options))  # pass to default hook
  }
  x <- unlist(strsplit(x, "\n"))
  more <- "..."
  if (length(lines)==1) {        # first n lines
    if (length(x) > lines) {
      # truncate the output, but add ....
      x <- c(head(x, lines), more)
    }
  } else {
    x <- c(more, x[lines], more)
  }
  # paste these lines together
  x <- paste(c(x, ""), collapse = "\n")
  hook_output(x, options)
})
``` 


## routlier

routlier is a package that is built to look for outliers in a dataset. The functions allow a user to look for outliers that are 'x' number of deviations away from the mean in the data for a particular column. The number of 'Outliers' in a dataset will be returned. Additionally any Outlier value will now be replaced with the word 'Outlier' in the dataset. 

```{r detroit}
library(routlier)

routlier::routlier_simple(data = detroit,sd = 1)

```

## routlier:: Example with both quantitative and qualitative data

Here we will utilize the student dataset that is included in the **routlier** package. This dataset has both quantitative and qualitative data in it. You can see we have **274 outliers** when we set the **sd** argument equal to **2**.

```{r, output.lines=16}

routlier_simple(data = student,sd = 2)

```

## routlier:: Using routlier_dt_sd() we can find the **Outliers** in a data set and have them highlighted with a green background to make them easier to find. Here we have an interactive DT::table that gets returned. This allows us to filter and sort out data much more easily.

```{r}

routlier_dt_sd(data = detroit,sd = 1)
```


## routlier:: Using routlier_rh_sd() we can find the **Outliers** in a data set and have them highlighted with a green background to make them easier to find.

```{r}

routlier_rh_sd(data = detroit,sd = 1)
```
